---
title: "Shiny Application and Reproducible Pitch"
author: "Alexis Parker"
date: "2023-01-20"
output: ioslides_presentation
---

## Information About App

```{r, warning=FALSE, results='hide', message=FALSE, echo=FALSE}
library(ggplot2)
library(dplyr)

```

-   Dataset: diamonds {ggplot2}
-   There are seven variables
    -   carat, depth, table, price

    -   x, y, z
-   There are three inputs
    -   X Variable

    -   Y Variable

    -   Number of Clusters

## How to Use the App

-   Input
    -   Select an X variable ()

    -   Select an Y variable

    -   Select the number of clusters (Min = 1 and Max = 5)
-   Output
    -   A K-means clustering plot (Shown in the next slide)

## Plot Preview

```{r, results='hide', echo=FALSE}
data("diamonds")
vars <- names(diamonds[,c(-2,-3,-4)])
DiamondData <- diamonds[, c(vars)]
clusters <- kmeans(DiamondData, centers = 3)
```

```{r}
plot(DiamondData$carat, DiamondData$price, col = clusters$cluster, 
     pch = 19, cex = 3, xlab = "carat", ylab = "price")  
palette(c("#11ACEF","#037A03","#D10D0D"))
```

## Link to App and Github

App: [Click Here](https://tqzbv6-alexis-parker.shinyapps.io/Kmeans-Cluster/?_ga=2.219751257.134192892.1674251573-720519868.1674251573)

Git: [Click Here](https://github.com/aparker03/Shiny-Application-and-Reproducible-Pitch)
